### 2022-03-10 ch1.tex
3 article summaries

\section{Background}

\subsection{Information Flow}
% what happened before this point? 
A critical turning point in the study of the flow information was put forth by
renowned Sociologist Paul Lazarsfeld \citeyearpar{lazarsfeldPeopleChoice1944}.
Lazarsfeld and others theorized that the media did not directly influence the
masses, but that a "Two-Step Flow" was occurring where "opinion leaders"
interpreted messages from mass media and then, in turn, promoted their opinions
to the masses \citep{katzPersonalInfluencePart1955}. The opinion leaders
interpret, explain, and diffuse contents to "opinion followers". From a networks
perspective, "people rarely act on mass-media information unless it is also
transmitted through personal ties" \citep[p. 1374]{granovetterStrengthWeakTies1973}. 
Lazarsfeld \citeyearpar{lazarsfeldPeopleChoice1944}'s first study focused on
politics but follow up studies from \citep{katzPersonalInfluencePart1955} showed
that this model matched information flows beyond the political realm. In
contrast to the one-step flow, where media directly influences the masses,
Lazarsfeld's theory remains in prominence today. While many scholars assumed
that modern micro-targeted marketing strategies would provide evidence for a
one-step flow perspective \citep{bennettOneStepFlowCommunication2006}, many
scholars find that "opinion leaders" (often influencers and celebrities) still
create a two-step flow of information transmission \citep{choi15,
hilbertOneStepTwo2017}.

@@

The digital age did not only revolutionize communication. It also
revoluitionized information search \citep{ramirez2002information}. Just as prior
to the digital age you could open an encyclopedia or peruse the library to find
the information you seek, much of the computer-mediated information search
surely occurs outside of social network activation contexts. While searching in
an encyclopedia is far less common today, internet search engines have
revolutionizes the speed and ease at which we can find information. Early web
search engines allowed information seekers to browse web directories and early
engines like Yahoo! and Altavista found success using keyword-based search,
though the early algorithms were limited in what they could find and relied
heavily on the wording of the queries. Google, the major web search engine used
today, introduced the disrputive PageRank algorithm in the early 2000s, securing
its place as the information hegemon of the 21st century
\citep{brin1998anatomy}. Not only has computer-mediated information search
revolutionized the ease of obtaining information, but it has also changed out
brains. \citet{sparrow2011google} show that the digital age has led to worse
memory and higher reliance on technology to keep track of information for us.
These search engines have also shaped our cultures by controlling, whether
through algorithm or intentionally, the information the engine provides. For
example, Google will not show results for various neo-Nazi websies in countries
where holocaust denial is illegal, like France and Germany. This is illustrative
of the control engines have over information and how this control may introduce
various political, economic, and social biases in the information they provide
\citep{segev2010google}. When 99Firms \citeyearpar{99firms22} compiled the data
from sources like NetMarketShare, Statista, DuckDuckGo, Yahoo Finance, Google,
and Pew Research they find that about about Around 93\% of all web traffic is
via a search engine and that 78.39\% of all internet search use Google. Because
computer-mediated information search is instantaneous and only requires mobile
data or wifi, there is virtually no cost to seeking information on one of these
mediums.

@@

\section{Broader Impact}
\begin{center}
    \texttt{UNDERGOING CHANGES}
\end{center}

@@

\begin{center}
    \texttt{all three of these are UNDERGOING CHANGES}
\end{center}

To make my intended contributions to the literatures on computational
social science, sociological methodology, social norms, social networks,
and diffusion, my dissertation will take the following format:

% todo, go over fig:conceptmap

- How can we operationalize Google Search Trends as a valid indicator for uses in social science research?

I will first investigate how Google Search Trends can be operationalized
as cultural attitudes, disease prevalence and voting behaviors through
comparing trends data to observed valid indicators of these cases.
Specifically, I will test cultural indicators from the NORC General
Social Survey, United States county-level suicide rates from National
Center for Health Statistics, US case rates of Covid-19 from The New
York Times, historical US Presidential Election results, and the
American National Election Survey against selected Google Trends terms
and analyze the data using correlation methods. The aim of this article
is to assess the construct validity and will contribute to critical big
data studies and sociological methodology.

Computational social science and other disciplines are quick to 
adopt new sources of digital trace data for use in academic research. 
In this article, I examine the validity of Google Search Trends 
as potential indicators of three different cases, namely attitudes, 
disease prevalence and political preferences using eight %TODO double check number
different validated data sources. I use Pearson and Repeated Measures Correlations 
between the Google Trends and the validated indicators as well as multiple linear regression
(for cross-sectional datasets) and random intercept hierarchical linear models
(for longitudinal datasets) as additional tests of the data. 
I fail to find correlation among any of the Google 
Trends tested and their validated indicators. While some Google Trends 
tested were significantly associated with the outcome in the regression models,
effects tended to be small and the total model interpretability remained low,
even when controlling for demographic variables. This article shows that there is no 
external validity of Google Trends for these uses and social scientists
will find no replacement for high quality survey data with Google Trends.

- How do computer-mediated or interpersonal information-seeking strategies vary
across populations?
- What factors lead people to perform health information search on the Covid-19 vaccine online versus among social network ties?

The second article in my dissertation investigates the question "what
are the behavioral processes that lead to macro-level outcomes" (in this
case, Google Trends results) proposed by \citet{breigerScaling2015}. Knowing that
Google trends data only encompasses a small portion of the
information-seeking done by modern humans, it is important to
investigate what leads individuals to search for a question online using
a search engine (contributing to macro-level trends data) versus more
traditional means of information gathering, such as network activation
(asking someone in their social network for informational support). To
investigate this, I use the case of receiving, requesting, and sharing
information about the Covid-19 vaccine in a survey I received funding to
conduct of 900 Adults in the United States.

Previous research has greatly failed to distinguish between the activation of
information seeking behaviors online and offline. Using theories of social
support and uses and gratifications theory I investigate the factors associated
with each vehicle type when on information seeking vehicle: personal connection,
doctor, social networking site, online forum, and online search engine. Using
novel survey data of % TODO  nrow(rain) Americans and their experience seeking out
information about the Covid-19 vaccines, I find little evidence that online
search is more utilized than seeking social support from personal network
connections or health professionals. I find evidence that the vehicles queried
in this survey are conceptually different and that the utilization of different
vehicles varies by demography and information sources. Finally, I find that
different fountains of information and information search vehicles hold real
world consequences through their associations with Covid-19 vaccination rates
and intentions, as information from a doctor increased the Covid-19 vaccination
uptake while receiving information from a Social Networking Site like Facebook
or Twitter was associated with lower odds of vaccination.

- How are new health behavior norms regarding public health recommendations formed during the Covid-19 pandemic?  
- How are patterns of information-search related to social norm stabilization during the Covid-19 pandemic?

My final article takes a deeper dive into the formation of social norms
governing health behaviors in cases of extreme uncertainty using the cases of
both a) population mobility during early 2020 and b) vaccination rates during
early 2021, both as responses to public health recommendations to mitigate the
Covid-19 pandemic. Using theories of associative diffusion and the integrated
theoretical framework of norms, I test how these health behaviors are outcomes
of assortative signaling from networks and other sources, such as social
isolation and connection between communities, religious and political
conservativism, and attention to media sources, and online norms as measured by
information-search behaviors. To investigate this, I conduct statistical
modelling on a dataset I compiled from multiple sources, including Google,
Facebook, and the Center for Disease Control and Prevention.

This paper examines how social norms are formed under conditions of uncertainty
using the case studies of stay-at-home and vaccination rates during the Covid-19
pandemic.  I test fear-based models of behavioral adaption to public health
recommendations as well as patterns of complex social contagion using linear
mixed effects models. These models show that complex contagion is a valid
framework for the social contagion of new norms during Covid-19. However, I find
important moderating effect of signal discordance, the contextual diversity of
signals received by an ego.

>>>>

\section{Theoretical Underpinnings}

\subsection{Information Flow}
% TODO what happened before this point? 
A critical turning point in the study of the flow information was put forth by
renowned Sociologist Paul Lazarsfeld \citeyearpar{lazarsfeldPeopleChoice1944}.
Lazarsfeld and others theorized that the media did not directly influence the
masses, but that a "Two-Step Flow" was occurring where "opinion leaders"
interpreted messages from mass media and then, in turn, promoted their opinions
to the masses \citep{katzPersonalInfluencePart1955}. The opinion leaders
interpret, explain, and diffuse contents to "opinion followers". From a networks
perspective, "people rarely act on mass-media information unless it is also
transmitted through personal ties" \citep[p. 1374]{granovetterStrengthWeakTies1973}. 
Lazarsfeld \citeyearpar{lazarsfeldPeopleChoice1944}'s first study focused on
politics but follow up studies from \citep{katzPersonalInfluencePart1955} showed
that this model matched information flows beyond the political realm. In
contrast to the one-step flow, where media directly influences the masses,
Lazarsfeld's theory remains in prominence today. While many scholars assumed
that modern micro-targeted marketing strategies would provide evidence for a
one-step flow perspective \citep{bennettOneStepFlowCommunication2006}, many
scholars find that "opinion leaders" (often influencers and celebrities) still
create a two-step flow of information transmission \citep{choi15,
hilbertOneStepTwo2017}.

@@

The digital age did not only revolutionize communication. It also
revoluitionized information search \citep{ramirez2002information}. Just as prior
to the digital age you could open an encyclopedia or peruse the library to find
the information you seek, much of the computer-mediated information search
surely occurs outside of social network activation contexts. While searching in
an encyclopedia is far less common today, internet search engines have
revolutionizes the speed and ease at which we can find information. Early web
search engines allowed information seekers to browse web directories and early
engines like Yahoo! and Altavista found success using keyword-based search,
though the early algorithms were limited in what they could find and relied
heavily on the wording of the queries. Google, the major web search engine used
today, introduced the disrputive PageRank algorithm in the early 2000s, securing
its place as the information hegemon of the 21st century
\citep{brin1998anatomy}. Not only has computer-mediated information search
revolutionized the ease of obtaining information, but it has also changed out
brains. \citet{sparrow2011google} show that the digital age has led to worse
memory and higher reliance on technology to keep track of information for us.
These search engines have also shaped our cultures by controlling, whether
through algorithm or intentionally, the information the engine provides. For
example, Google will not show results for various neo-Nazi websies in countries
where holocaust denial is illegal, like France and Germany. This is illustrative
of the control engines have over information and how this control may introduce
various political, economic, and social biases in the information they provide
\citep{segev2010google}. When 99Firms \citeyearpar{99firms22} compiled the data
from sources like NetMarketShare, Statista, DuckDuckGo, Yahoo Finance, Google,
and Pew Research they found that about about Around 93\% of all web traffic is
via a search engine and that 78.39\% of all internet search use Google. Because
computer-mediated information search is instantaneous and only requires mobile
data or wifi, there is virtually no cost to seeking information on one of these
mediums.

@@

To investigate information-seeking behaviors, online search tools, and how
new norms in health behaviors form, I first provide an outline of the 
information push and pull process in figure \ref{fig:concept-map}. After 
being exposed to new information, an actor can choose to further investigate
the information online or offline and, in turn, further share the 
information they were exposed to.

This dissertation uses three articles to investigate different parts of
the aforementioned theoretical framework (figure \ref{fig:concept-map}).
The dissertation is divided into three parts, with Article 1 focusing 
on online information search, Article 2 focusing on online and offline
information search, and Article 3 investigating the entire information
push and pull process in the context of establishing new norms.

Computational social science and other disciplines are quick to adopt new
sources of digital trace data for use in academic research. In this article, I
examine the validity of one of these new sources, Google Search Trends. I
validate how Google Trends can be used to demonstrate three different cases,
namely attitudes, disease prevalence and political preferences using eight %TODO double check number
different validated data sources. This paper asks, "How can we operationalize
Google Search Trends as a valid indicator for uses in social science research?"
I use Pearson and Repeated Measures Correlations between the Google Trends and
the validated indicators as well as multiple linear regression (for
cross-sectional datasets) and random intercept hierarchical linear models (for
longitudinal datasets) as additional tests of the data.

I fail to find correlation among any of the Google Trends tested and their
validated indicators. While some Google Trends tested were significantly
associated with the outcome in the regression models, effects tended to be small
and the total model interpretability remained low, even when controlling for
demographic variables. This article shows that there is no external validity of
Google Trends for these uses and social scientists will find no replacement for
high quality survey data with Google Trends.

Knowing that Google trends data only encompasses a small portion of the
information-seeking done by modern humans, it is important to
investigate what leads individuals to search for a question online using
a search engine (contributing to macro-level trends data) versus more
traditional means of information gathering, such as network activation
(asking someone in their social network for informational support). 
Previous research has greatly failed to distinguish between the activation of
information seeking behaviors online and offline. Using theories of social
support and uses and gratifications theory, I investigate the factors associated
with each vehicle type when on information seeking vehicle: personal connection,
doctor, social networking site, online forum, and online search engine. I use
original survey data of 948 Americans to investigate their experiences seeking out
information about the Covid-19 vaccines.

This paper aims to address two main questions:
\begin{itemize}
  \item How do computer-mediated or interpersonal information-seeking strategies vary
across populations?
  \item How does the information search vehicle utilized affect Covid-19 Vaccination uptake? 
\end{itemize}

In this article, I find little evidence that online search is more utilized than
seeking social support from personal network connections or health professionals
as I hypothesize based on uses and gratifications theory. I find evidence that
the categorizations of vehicles queried in this survey are indeed conceptually
different from each other and that the utilization of different vehicles varies
by demography and information exposure points. Finally, I find that different
exposure points and information search vehicles hold real world consequences
through their associations with Covid-19 vaccination rates and intentions, as
information from a doctor increased the Covid-19 vaccination uptake while
receiving information from a Social Networking Site like Facebook or Twitter was
associated with lower odds of vaccination.

My final article takes a deeper dive into the formation of social norms
governing health behaviors in cases of extreme uncertainty using the cases of
both stay-at-home rates and vaccination rates as responses to public health recommendations to mitigate the Covid-19 pandemic. Using theories of associative diffusion and the integrated
theoretical framework of norms, I test models of behavioral adaption to public health
recommendations as well as patterns of complex social contagion using linear
mixed effects models.

These models show that complex contagion is a valid 
framework for the social contagion of new norms during Covid-19. Importantly, I find
important moderating effect of signal discordance, the contextual diversity of
signals received by an ego. This paper shows that the contagion process is not
fully understood without looking at the context of each exposure point within the
range of exposures one experiences.

\section{Contributions and Future Directions}
\begin{center}
    \texttt{UNDERGOING CHANGES}
\end{center}

@@

\section{Conclusions}
\begin{center}
    \texttt{UNDERGOING CHANGES}
\end{center}

what do these papers come TOGERTHER to tell us about information search?
